---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# filenamr

<!-- badges: start -->
`r badger::badge_lifecycle("experimental")`
`r badger::badge_license("MT", "blue", "https://cran.r-project.org/web/licenses/MIT")`
<!-- badges: end -->

The goal of filenamr is to ...

## Installation

You can install the development version of filenamr like so:

``` r
pak::pkg_install("elipousson/sfext")
```

## Making file names

The `make_filename()` function is design for creating structured file names based on a name and optional label, prefix, or postfix:

```{r example}
library(filenamr)

make_filename(
  name = "Neighborhoods",
  label = "Baltimore, MD"
)

make_filename(
  prefix = "Plot",
  name = "Neighborhoods",
  label = "Baltimore, MD"
)

make_filename(
  prefix = "date",
  name = "Neighborhoods",
  label = "Baltimore, MD",
  postfix = "map",
  fileext = "jpeg"
)
```

You can also pass a filename with an extension or path (setting `create = TRUE` to create a directory if no directory already exist):

```{r}
make_filename(
  filename = "baltimore_neighborhoods",
  path = "data",
  fileext = "pdf",
  create = FALSE
)
```

If you provide a number as part of a filename, you can use the increment parameter to create a filename where the number is replaced with a larger number: 

```{r}
make_filename(
  filename = "plot",
  postfix = "1",
  increment = TRUE,
  fileext = "png"
)

make_filename(
  filename = "plot",
  postfix = "1",
  increment = 2,
  fileext = "png"
)
```

## Working with file metdata

This package uses the exiftoolr package (installing the development version on GitHub is recommended) to support reading and writing EXIF, IPTC, and XMP-DC metadata.
